CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-11-28 paper.Rmd
head(as.data.frame(psut)) to avoid nonprinting "i"

```{r}
# (5) Review results using the pins package.
#     Establish the pinboard.
pinboard <- file.path("ExampleFolder", "OutputData", "PipelineReleases") |> 
  pins::board_folder(versioned = TRUE)
#     Look at the psut data frame
#     created by the PFUDatabase pipeline.
psut <- pinboard |>
  pins::pin_read(name = "psut", version = "20230811T122618Z-3b7b3")
head(psut)
#     Each column of the psut data frame contains sparse matrices, 
#     the columns of which are suppressed on display.
#     Show the column names here.
colnames(psut$R[[1]])
#     Show an example resource (R) matrix.
psut$R[[1]]

>>>>

```{r}
# (5) Review results using the pins package.
#     Establish the pinboard.
pinboard <- file.path("ExampleFolder", "OutputData", "PipelineReleases") |> 
  pins::board_folder(versioned = TRUE)
#     Look at the psut data frame
#     created by the PFUDatabase pipeline.
psut <- pinboard |>
  pins::pin_read(name = "psut", version = "20230811T122618Z-3b7b3")
head(as.data.frame(psut))
#     Each column of the psut data frame contains sparse matrices, 
#     the columns of which are suppressed on display.
#     Show the column names here.
colnames(psut$R[[1]])
#     Show an example resource (R) matrix.
psut$R[[1]]
